\documentclass[11pt]{article}

\newcommand{\TITLE}{Chimbuko: CODAR Framework for Performance Analysis and Visualization-- YEAR 2
}
\newcommand{\AUTHORS}{Kerstin Kleese Van Dam, Shinjae Yoo, Wei Xu,\\ Line Pouchard, Hubertus Van Dam, Li Tang, Dingwen Tao, Cong Xie, Abid Malik\\ Brookhaven National Laboratory\\ \\ Kevin Huck, Sameer Shende\\ University of Oregon\\}

\input{preamble}

\title{\TITLE{}}
\date{}
\author{\AUTHORS{}}

\begin{document}
\pagestyle{empty}

\input{header}

\newpage

\renewcommand{\contentsname}{{\huge Table of contents}}

\tableofcontents

\clearpage
\maketitle

\pagestyle{plain}
\setcounter{page}{1}

\input{Narrative/introduction}
\input{Narrative/stakeholders}
\input{Narrative/usecases}
\input{Narrative/requirements}
\input{Narrative/related}
\input{Narrative/design}
\input{Narrative/metrics}
\input{Narrative/workplan}
\input{Narrative/questions}

\clearpage
%\bibliographystyle{ieeetr}
%\bibliography{Bibs/z-checker.bib}
\begin{thebibliography}{1}

  \bibitem{kerstin2015design}{\em {Enabling Structured Exploration of Workflow Performance Variability in Extreme-Scale Environments}}:
  {Kleese van Dam, K., Stephan, E.G., Raju, B., Altintas, I., Elsethagen, T.O., and Krishnamoorthy, S.}, {Proc. $8^{th}$ Workshop in Many-Task Computing on Clouds, Grids, and Supercomputers (MTAGS) collocated with SC 2015}.
  
  \bibitem{sonar} {\em Lammel S., Zahn F., Fröning H. (2016) SONAR: Automated Communication Characterization for HPC Applications. In: Taufer M., Mohr B., Kunkel J. (eds) High Performance Computing. ISC High Performance 2016.}
  
 \bibitem{TAU} {\em S. Shende, A. D. Malony, J. Cuny, K. Lindlan, P. Beckman and S. Karmesin, Portable Profiling and Tracing for Parallel Scientific Applications using C++, Appears in: Proceedings of SPDT'98: ACM SIGMETRICS Symposium on Parallel and Distributed Tools, pp. 134-145, Aug. 1998.}
 
 \bibitem{ScoreP}{\em Knüpfer A. et al. (2012) Score-P: A Joint Performance Measurement Run-Time Infrastructure for Periscope, Scalasca, TAU, and Vampir. In: Brunst H., Müller M., Nagel W., Resch M. (eds) Tools for High Performance Computing 2011. }
 
 \bibitem{HPCToolkit} {\em L. Adhianto, S. Banerjee, M. Fagan, M. Krentel, G. Marin, J. Mellor-Crummey, and N. R. Tallent. HPCToolkit: Performance tools for scientific computing. In SC '08: Proc. of the 2008 ACM/IEEE Conference on Supercomputing, New York, NY, USA, 2008. ACM.}
 
 \end{thebibliography}
\end{document}

